Ice sheet mass flows

### 2024-06-07 sankey.tex
vMLfd unused

    \sankeyset{
      def data/.code args={#1/#2/#3}{% node name/label/values
        \LabSet{#1}{#2}
        \QSet{#1}{#3}
        \typeout{#1: \Q{#1} Gt (\Lab{#1})}
      },
      def data/.list={
        %% INSERT_CSV_HERE
        %% COMPUTED 
        {vML/Mass loss/
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRET}+\Q{vGZRET}+\Q{vEV})-
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP})},
        {vMLfd/Mass Loss fixed domain/\Q{vML}-(\Q{vFRET}+\Q{vGZRET})},
        {vMG/Mass gain/
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP})-
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRET}+\Q{vGZRET}+\Q{vEV})}
      },
    }

>>>>

    \sankeyset{
      def data/.code args={#1/#2/#3}{% node name/label/values
        \LabSet{#1}{#2}
        \QSet{#1}{#3}
        \typeout{#1: \Q{#1} Gt (\Lab{#1})}
      },
      def data/.list={
        %% INSERT_CSV_HERE
        %% COMPUTED 
        {vML/Mass loss/
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRET}+\Q{vGZRET}+\Q{vEV})-
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP})},
        {vMG/Mass gain/
          (\Q{vSF}+\Q{vRF}+\Q{vCD}+\Q{vDP})-
          (\Q{vSU}+\Q{vRU}+\Q{vBM}+\Q{vDYN}+\Q{vFRET}+\Q{vGZRET}+\Q{vEV})}
      },
    }
